---
title: "examples"

output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
install.packages("eRm")
install.packages("RMX")
library(eRm)
library(RMX)
```

## R Markdown

For our example we will use the included dataset big5. It's simulated after a students survey of the BIG 5 (Openness [O], Conscienciousness [C], Extraversion [E], Agreeableness [A], and Neuroticism [N]). The scale comprises 21 items following the structure of the BFIK. The items were originally presented in German. See `?big5` for a translation and more details.

Let's have a look at the Extraversion scale first.

```{r cars}
dat_extra = big5[, c(1, 6, 11, 16)]
```

First, we must estimate a model, in this case the Partial Credit Model. We will use the `eRm`-Package, however you could use one of the other available packages as well.

```{r}
res0 = PCM(dat_extra)
```

That's it, now we can use the `plotPIccc`-function to display the model graphically in many different ways. Let's have a look at the standard functionality first:

```{r}
plotPIccc(res0)
```

