---
title: "examples"

output: rmarkdown::html_vignette
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
install.packages("eRm")
install.packages("RMX")
library(eRm)
library(RMX)
```
# TODOS
we oder you, es ist bisschen beides drin grade

plotPIccc-function oder plotPIccc function

# R Markdown

For our example we will use the included dataset big5. It's simulated after a students survey of the BIG 5 (Openness [O], Conscienciousness [C], Extraversion [E], Agreeableness [A], and Neuroticism [N]). The scale comprises 21 items following the structure of the BFIK. The items were originally presented in German. See `?big5` for a translation and more details.

Let's have a look at the Extraversion scale first.

```{r cars}
dat_extra = big5[, c(1, 6, 11, 16)]
```

First, we must estimate a model, in this case the Partial Credit Model. We will use the `eRm`-Package, however you could use one of the other available packages as well.

```{r}
res0 = PCM(dat_extra)
```

That's it, now we can use the `plotPIccc`-function to display the model graphically in many different ways. First, let's have a look at the classical Person-Item Map, which can also be plotted by using `classical = TRUE`.

```{r}
plotPIccc(res0, classical = TRUE, extwin = FALSE)
```


# One function and several items

By default, `plotPIccc()` draws the Category Characteristic Curves (CCCs) for all items. Let's have a look at the standard functionality first:

```{r}
plotPIccc(res0, extwin = FALSE)
```

In this PIccc we find four areas of output: the top left segment shows the person parameter histogram. The green line is the test information function (TIF) and the red line the standard error (SE). The top right segment holds the legend. The lower right segment shows the category response frequency barcharts of each item. The lower left segment is the most important segment. It shows the item-related functions, in this case the CCCs.

The plot is highly customizable. For example, if you wish to just show the person parameter histogram and the CCCs, you can do so by setting `funwprop = 1`. Use 0 if you just want to show the barplots on the right. In the same way, you can just show the CCCs and barplots without the person parameters by using `funhprop = 1`. You can also use values between 0 and 1 for different proportions.

```{r figures-side, fig.show="hold", out.width="50%"}
plotPIccc(res0, funwprop = 1, extwin = FALSE)
plotPIccc(res0, funhprop = 1, extwin = FALSE)
```

MEHR BEISPIELE UND DANN

# One item and several functions

So far we have only looked at one of the two modi the `plotPIccc` function offers: plotting one type of curve for a set of items. In many cases however, a particular item merits a closer examination. You can do so by simply setting the `isel` argument to the desired item. Let's look at item "Q6" and plot alle possible function types.

```{r}
plotPIccc(res0, isel = "Q6", type = c("CCC", "TCC", "IIF", "CIF", "BIF"),
          extwin = FALSE)
```

In this modus the output looks slightly different than before. The upper left segment is still composed of the person parameter histogram as well as the TIF and SE. However, because only a subset of items was used, dashed lines indicate the TIF and SE of only the selected items. The lower left segment now shows the different functions for item "Q6". The top right segment shows the barplot of this item, while the lower right segment displays the legends of the respective functions. Of course, every argument we used before can also be used in this modus.
